%\chapter*{ACKNOWLEDGMENT}       
\begin{titlepage}

\begin{center}
    \Large
    \vspace{0.9cm}
    \textbf{ACKNOWLEDGMENT}
    \end{center}

     \justify \hspace{1cm} First and foremost, thanks to Allah for blessing us and endowing us with health, patience and knowledge to complete this work.
    \par
    \justify \hspace{1cm}  Our work in this project comes after semesters of good preparation and hard work during our journey in Computer \& Automatic Control Engineering Department. So, We firstly should thank all of our professors and academic staff for all of their help over the past five years. They have been a great source of support and encouragement. They have always made themselves available when it was needed and provided good advice.
    \par
    \justify \hspace{1cm} We would like to sincerely thank our supervisor \textbf{Dr. Mohamed Arafa} for his support to our team, for his advice and for providing us with information and resources to do our work in this project.
    \par
    \justify \hspace{1cm} Special thanks to \textbf{Eng. Muhammad Shehab} for his support and guidance from the beginning. He has provided us with knowledge required to complete this project and believed that we would reach this point successfully.
    \par
    \justify \hspace{1cm} For being an industrial partner responsible for project technical support, we would like to thank \textbf{Valeo company} and express our special appreciation to \textbf{Eng. Muhammad Zahran} who always supported us with useful technical consultancies as project monitor from valeo.
    \par
    \justify \hspace{1cm} Finally, we would also like to express our gratitude for everyone who helped us during our graduation project.
\end{titlepage}

