\newline
\newline
\vspace{3mm}
\hfill

\section{Conclusions}
\hspace{2cm}Automating the delivery process has been regarded as a significant topic in research due to its importance in real world applications. This project was our chance to leave a footprint in this topic and we concluded the following: The importance and the huge effect that ROS (Robot Operating System) has, Allowing us to remove and attach as many components to the system as we need, Making the system flexible and easily scalable, also facilitating module-to-module communication lifting up the overhead of implementing reliable communication modules, Leaving up to focus on our main work. The possibility of implementing a controller that is a mixture of both: Classical and Neural Network modules without the need of implementing a full end-to-end controller at the moment, as the implementation of end-to-end controller would require more time and huge amount of data to be collected.
\section{Future Work}
\hspace{2cm}For the future we have in mind multiple ideas, that could be put in motion to improve our current system's service, In this section we introduce some of these ideas from both: technical and business point of views.\\
\textbf{Technical-wise}\\
From technical point of view we can improve our system by achieving the following:
\begin{enumerate}
    \item Implementation of a subtle vehicle-to vehicle communication to propagate information faster through the system.
    \item Improving the current database to handle vast number of mobile robots operating at the same time.
    \item Modifying the robot to work in more chaotic environment by implementing full end-to-end robot 
    controllers. 
    \item Reducing the time of delivery by increasing the accuracy of both the path planning and the neural network modules.
    \item Enhancing the quality of our customers' service by adding more features to the currently used E-commerce system (Website and Mobile Application).
\end{enumerate}
\newpage
\textbf{Business-wise}\\
From business point of view we can improve our business by achieving the following:
\begin{enumerate}
    \item Building a fleet of self-driving robots, Covering a wider delivery zone subsequently increasing our service availability.
    \item Deploying our system to a production suitable components instead of the currently used high-cost development components. 
    \item Attracting more vendors to contract with us to use or service in selling and delivering their products. 
    \item Building a concrete long-term marketing strategy to spread the acceptance of self-driving robots and increase our customers base.
\end{enumerate}